---
title: "Group2 Strawberry Data"
author: "Shuting Li, Lauren Temple, Zening Ye, Keliang Xu"
date: "11/1/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
pacman::p_load('ggplot2', 'plotly', 'dplyr', 'magrittr', 'tidyverse', 'maps', 'knitr', 'knitrExtra')
source(file= 'Slidescript.R')
```

## Overview

- How toxic are the chemicals on our strawberries
- Each chemicals human toxicity level
- Amount of each chemical being used

## Definition of Toxicity
- Highly toxic for humans
  - Carcinogen = known or 
  - Neurotoxins = present or 
  - Developmental or Reproductive Toxins = present
- Moderately toxic for human
  - Carcinogen = probable/possible and 
  - Hormone Disruptor = suspect
- Slightly toxic for human
  - Carcinogen= possible/possible or 
  - Hormone Disruptor = suspect
  - Only one not both

## Map

```{r, echo=FALSE}
usamap<-function(){
  usa_map <- map_data("state")
  states<-c("California","Florida","Oregon","Washington")
  region<-tolower(states)
  tmp<-data.frame(cbind(states,region))
  gg <- ggplot()
  gg <- gg + geom_map(data=usa_map, map=usa_map,
                    aes(long, lat, map_id=region),
                    color="black", size=0.15, fill=NA)
  gg <- gg + geom_map(data=tmp, map=usa_map,
                    aes(fill=states, map_id=region),
                    color="black", size=0.15)
  gg
}
```

```{r}
usamap()
```


## Plot of Chemical Use by State

```{r}
ggplotly(Plot)
```

## How much of these chemicals are being used?

- Focused on chemical applications measured in lb's
  - Filtered out some entries that were missing values
- Left us with three states: California, Florida, Washington

## Chemcial usage in Lbs
```{r, echo=FALSE}
pestiToxin("CALIFORNIA")
```

## Chemcial usage in Lbs
```{r, echo=FALSE}
pestiToxin("FLORIDA")
```

## Chemcial usage in Lbs
```{r, echo=FALSE}
pestiToxin("WASHINGTON")
```

## Captan
- Captan is a highly toxic chemical and it is used in large amounts
- Probable carcinogen
- Short term dermal exposure may cause dermatitis and conjunctivitis in humans
- Ingestion of large quantities of captan may
cause vomiting and diarrhea in humans
- Long term effects on humans are unknown

## Data Sources
- https://quickstats.nass.usda.gov/#56E84525-1350-34A1-9ED7-27363BD5A7D3
- https://www.epa.gov/sites/default/files/2016-09/documents/captan.pdf
