---
title: "Group2-EDA"
author: "Shuting Li, Lauren Marie, Zening Ye, Keliang Xu"
date: "10/25/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
webshot::install_phantomjs()
library(tidyverse)
library(magrittr)
library(dplyr)
```

# Clean data

## import original data
```{r}
strawb <- read_csv("data/Strawberries.csv")
pesti <- read_csv("data/Pesticides.csv")
```

## data cleaning about strawb.csv

### drop all NA columns
```{r}
drop_na_info <- function(df){
  cnames = colnames(df)
  T = NULL
  for(i in 1:ncol(df)){T <- c(T, nrow(unique(df[i])))}
  drop_cols <- cnames[which(T == 1)]
  return(dplyr::select(df, !all_of(drop_cols)))
}

strawb1 <- drop_na_info(strawb)

colnames(strawb1)
```
After droping NA columns, we get strawb1 with 10 columns.


### Separate ‘Data Item’ into 4 columns
```{r}
strawb1 %<>% separate(col = 'Data Item', into = c("Strawberries", "Items", "Discription", "Units"),sep = ",",fill = "right")

distinct(strawb1, Strawberries)

distinct(strawb1, Items)

distinct(strawb1, Discription)

distinct(strawb1, Units)
```
Separate ‘Data Item’ into "Strawberries", "Items", "Discription", "Units".


### Separate ‘Domain’ into 2 columns
```{r}
strawb1 %<>% separate(col = Domain, into = c("dname", "type"), sep = ",", fill = "right")

distinct(strawb1, dname)

distinct(strawb1, type)
```
Separate ‘Domain’ into "dname", "type".


### Separate 'Domain Category' into 2 columns
```{r}
strawb1 %<>% 
  mutate(Chemicals = `Domain Category`) %>%
  relocate(Chemicals, .after = `Domain Category`)

strawb1 %<>% 
  separate(Chemicals, into =c('Title', 'Details'), sep = ":", fill = "right")

distinct(strawb1, Details)

strawb1$Details <- str_replace(strawb1$Details, "\\(", "")
strawb1$Details <- str_replace(strawb1$Details, "\\)", "")

strawb1 %<>% 
  separate(Details, into = c('Chemical Name', "Number"), sep = "=", fill = "right")

distinct(strawb1, `Chemical Name`)
distinct(strawb1, Number)

strawb1$`Chemical Name` <- str_trim(strawb1$`Chemical Name`)
```
Replicate 'Domain.Category' to new variable and separate this new variable into 'Title', 'Details'. 

And then clean 'Details' and separate it into 'Chemical Name', "Number". Also captalize all words in 'Chemical Name'.


### drop useless columns
```{r}
drops <- c("Strawberries", "Domain Category")
strawb1 <- strawb1[ , !(names(strawb1) %in% drops)]
```
Drop "Strawberries", "Domain Category", because it is useless in data analysis.


## data cleaning about pesti.csv

### drop NA rows in pesti.csv and clean it
```{r}
pesti1 <- pesti %>% rename('Chemical Name' = Pesticide )

pesti1 %<>% filter(!is.na(pesti1))

pesti1$`Chemical Name` <- toupper(pesti1$`Chemical Name`)
```
Drop NA rows in pesti.csv, finally we get pesti1 with 45 rows.

And then rename 'Pesticide' to 'Chemical Name' and captalize all words in 'Chemical Name'.


### Define Human Toxins level
```{r}
pesti1 <- pesti1 %>% mutate('Human Toxins' = case_when(
  pesti1$Carcinogen == "known" | pesti1$Neurotoxins== "present" | pesti1$`Developmental or Reproductive Toxins`== "present" ~ "high" ,
  pesti1$Carcinogen == "possible" & pesti1$`Hormone Disruptor`=="suspected" & is.na(pesti1$Neurotoxins) & is.na(pesti1$`Developmental or Reproductive Toxins`)~ "moderate",
  pesti1$Carcinogen == "possible" & is.na(pesti1$`Hormone Disruptor`) & is.na(pesti1$Neurotoxins) & is.na(pesti1$`Developmental or Reproductive Toxins`)~ "slight",
  pesti1$Carcinogen == "probable" & is.na(pesti1$`Hormone Disruptor`) & is.na(pesti1$Neurotoxins) & is.na(pesti1$`Developmental or Reproductive Toxins`)~ "slight",
  is.na(pesti1$Carcinogen) & pesti1$`Hormone Disruptor`=="suspected" & is.na(pesti1$Neurotoxins) & is.na(pesti1$`Developmental or Reproductive Toxins`)~"slight"
))
```
Use columns 'carcinogen', 'Neurotoxins', 'Developmental or Reproductive Toxins' to define human toxins level.

High toxic for human: carcinogen = known or Neurotoxins = present or `Developmental or Reproductive Toxins` = present.

Moderate toxic for human: carcinogen = probable/possible and `Hormone Disruptor` = suspect.

Slight toxic for human: carcinogen= possible/possible or `Hormone Disruptor` = suspect, only one happens.


## wrangling two datasets
```{r}
strawbPesti <- inner_join(strawb1, pesti1,by="Chemical Name")

# Write the dataset into csv.
write_csv(strawbPesti, "strawbPesti.csv")
```
Combine two dataset into strawbPesti.csv by key column 'Chemical Name'. Only keep rows with known pesticides.



# Data Visualization
```{r}
pacman::p_load('ggplot2', 'plotly',"dplyr")
```

## clean strawbPesti.csv
```{r}
distinct(strawbPesti,State)
strawbPesti <- arrange(strawbPesti,`Chemical Name`)
#colnames(strawbPesti)
strawbPesti1 <- strawbPesti[,-13]
strawbPesti2 <- strawbPesti1[,c(2,4,7,12,13,20)]
strawbPesti3 <- filter(strawbPesti2, Discription==" MEASURED IN LB")
strawbPesti4 <- filter(strawbPesti3, Value !="(D)")
strawbPesti4$Value <- as.numeric(sub(",", "", strawbPesti4$Value, fixed = TRUE))
```
Only choose columns we will use: 'Year', 'State', 'Discription', 'Chemical Name', 'Value', 'Human Toxins'. Which is dataset "strawbPesti2".

We can see from strawbPesti2, values are different depend on measured methods for each chemical type in each state, so we can choose one method to go deep, finally we chose "MEASURED IN LB". Then we get dataset "strawbPesti3".

Then we drop no meaning rows of value. And change value into numeric variable. Finally we get dataset "strawbPesti4".


## show all states chemical usage value
```{r}
ggplot(strawbPesti4) + 
  geom_point(aes( x= `Chemical Name`, y= Value,col=Year)) + 
  facet_grid(`Human Toxins`~State)
```


## Chemical usage in California 
```{r}
cali <- filter(strawbPesti4,State=="CALIFORNIA")

# bar plot
calibar <- ggplot(cali)+
  geom_bar(mapping = aes(x=`Chemical Name`,y=Value,fill=`Year`), alpha = 4/5,stat = "identity")
ggplotly(calibar)

# polar plot
calibar + coord_polar()

## we can see which peti used more often in CALI throughout three years
```

